Legends for supplementary material

### 2019-05-16 Manuscript/Figures/figure_legends.Rmd
editted figure legends

**Figure 5. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

**Figure 6. Predictive importance.** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878. Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100. Transcription factors with higher values of predictive importance are denoted in dark red.

>>>>

**Figure 5. Predictive importance is outweighed by transcription factor binding sites.** Stacked barplots illustrating the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework, for each resolution on GM12878. Proportions are separated by the set of annotations included in the feature space including chromatin state segmentation, histone modification, and transcription factor binding sites.

**Figure 6. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for GM12878.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

**Figure 7. Predictive importance.** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for GM12878. Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100. Transcription factors with higher values of predictive importance are denoted in dark red.

### 2019-05-16 Manuscript/Supplementary/supplementary_legends.Rmd
editted figure legends

**Supplementary Figure 4. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

**Supplementary Figure 5. Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562. Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100. Transcription factors with higher values of predictive importance are denoted in dark red.

>>>>

**Supplementary Figure 4. Predictive importance is outweighed by transcription factor binding sites.** Stacked barplots illustrating the proportion of total predictive importance in models using optimal data level characteristics determined by the ensemble framework, for each resolution on K562. Proportions are separated by the set of annotations included in the feature space including chromatin state segmentation, histone modification, and transcription factor binding sites.

**Supplementary Figure 5. Comparing annotation-specific random forest models implemented on SMOTE re-sampled data with distance-type predictors for K562.** MCC performances were compared for models using specific groups of annotations as the feature space including: histone modifications (HM; red), chromatin state segmentations (CSS; green), transcription factor binding sites (TFBS; blue), and a feature space containing all 3 types combined (combined; purple). Each bar represents a model ran through the ensemble framework, with re-sampling technique and predictor-type characteristics fixed to SMOTE and distance-types. The error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosome.

**Supplementary Figure 6. Predictive importance** A heatmap illustrating the importance of the top 20 most predictive transcription factors for random forest models implemented on SMOTE resampled data with distance-type predictors for K562. Importances were sorted according to the 10 kb resolution and rescaled to values between 0 and 100. Transcription factors with higher values of predictive importance are denoted in dark red.
